Tor's Usability for Censorship Circumvention

### 2015-12-10 paper/circumvention-experiment.tex
delete phantom discussion section
finished linking resources

\section{Discussion}

\section{Resources}
\noindent Our online artifacts of the work done during this class, Fall 2015,
are below: 
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \href{https://github.com/lindanlee/circumvention-ux-tor}{github repo with experiment plans, code, and paper}
\item \href {https://github.com/lindanlee/circumvention-ux-tor/blob/master/pilot/1-strict.mp4}{pilot video 1}
	\href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/pilot/2-lax.mp4}{pilot video 2}
\item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/setup/setup-environment}{experimental setup code: firewall and screen capture} 
\item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/setup/takedown-environment}{experimental takedown code: saving files and cleanup} 
\end{itemize}

>>>>

\section{Resources}
\noindent Our online artifacts of the work done during this class, Fall 2015,
are below: 
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \href{https://github.com/lindanlee/circumvention-ux-tor}{github repo with experiment plans, code, videos, interviews, and much more}
\item \href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/videos}{qualitative interface evaluation videos}
\item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/sessions/pre/participant-summaries.txt}{summaries of qualitative interface evaluation videos}
\item \href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/notes}{qualitative interface evaluation interview notes}
\item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/setup/setup-environment}{experimental setup code: firewall and screen capture} 
\item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/setup/takedown-environment}{experimental takedown code: saving files and cleanup} 
\end{itemize}
